R Course Syllabus

### 2023-04-25 Bookdown Syllabus/Bookdown Syllabus.Rmd
Update to language in Rmds

Until now we have stored a single number, string, or TRUE/FALSE value in each object we created. But, if we were faced with a more complex problem, we could use vectors instead to solve it. Let's consider the task of figuring out who the tallest student is in a class. First, I'll generate some data. It is not important for you to know how to do this.

@@

We could get the number of snacks eaten by each student by going throw the indices of the two vectors one-by-one and summing the values like so:

>>>>

Until now we have almost always stored a single number, string, or TRUE/FALSE value in each object we created. But, if we were faced with a more complex problem, we could use vectors instead to solve it. Let's consider the task of figuring out who the tallest student is in a class. First, I'll generate some data. It is not important for you to know how to do this.

@@

We could get the number of snacks eaten by each student by going through the indices of the two vectors one-by-one and summing the values like so:
